\documentclass[journal, a4paper]{IEEEtran}

%\usepackage{cite}      
\usepackage{graphicx}
%\usepackage{psfrag} 
%\usepackage{subfigure} 
\usepackage{url}       
%\usepackage{stfloats} 


\begin{document}
	\title{Overview of Anime voice actor's social network and popularity.}
	\author{Florencia Zanollo
	\thanks{Advisor: Hideaki Takeda}}
	\markboth{markboth}{}
	\maketitle

\begin{abstract}
	Although Social Network of actors is a relatively common object of investigation that has been addressed many times; we can say that seiyuu (anime voice actors), come from a very different industry with a distinct way to relate to each other. \\
	In this research we use Wikidata and MyAnimeList to collect seiyuu information and build a Social Network. Topics explored:
	\begin{itemize}
	\item Structure and characteristics of seiyuu Social Network.
	\item Understanding what properties have a main role describing and predicting popularity of seiyuu.
	\item Compare prediction performances between different machine learning algorithms (and different models).
	\end{itemize}
\end{abstract}

\section{Introduction}
	% \PARstart{}{} creates a tall first letter for this first paragraph
	\PARstart{T}{ODO}.

% Main Part
\input{AnimeSeiyuuDataset.tex}
\input{SeiyuuSocialNetwork.tex}
\input{PopularityAnalysisAndPrediction.tex}

\section{Conclusion}
	This section summarizes the paper.

\begin{thebibliography}{5}
	%Each item starts with a \bibitem{reference} command and the details thereafter.
	\bibitem{HOP96} % Transaction paper
	J.~Hagenauer, E.~Offer, and L.~Papke. Iterative decoding of binary block
	and convolutional codes. {\em IEEE Trans. Inform. Theory},
	vol.~42, no.~2, pp.~429–-445, Mar. 1996.

	\bibitem{MJH06} % Conference paper
	T.~Mayer, H.~Jenkac, and J.~Hagenauer. Turbo base-station cooperation for intercell interference cancellation. {\em IEEE Int. Conf. Commun. (ICC)}, Istanbul, Turkey, pp.~356--361, June 2006.

	\bibitem{Proakis} % Book
	J.~G.~Proakis. {\em Digital Communications}. McGraw-Hill Book Co.,
	New York, USA, 3rd edition, 1995.

	\bibitem{talk} % Web document
	F.~R.~Kschischang. Giving a talk: Guidelines for the Preparation and Presentation of Technical Seminars.
	\url{http://www.comm.toronto.edu/frank/guide/guide.pdf}.

	\bibitem{5}
	IEEE Transactions \LaTeX and Microsoft Word Style Files.
	\url{http://www.ieee.org/web/publications/authors/transjnl/index.html}
\end{thebibliography}

\end{document}