\documentclass[11pt]{beamer}
\usetheme{Frankfurt}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{subcaption}
\usepackage[export]{adjustbox}

\setbeamercolor{emph}{fg=blue}
\renewcommand<>{\emph}[1]{%
  {\usebeamercolor[fg]{emph}\only#2{\itshape}#1}%
}
%-------------------------------------------------------------------------
\author{Florencia Zanollo - Adviser: Prof. Hideaki Takeda}
\title{Analysis of anime voice actor's social network and popularity}
%\setbeamercovered{transparent} 
%\setbeamertemplate{navigation symbols}{} 
%\logo{} 
\institute{University of Buenos Aires (Argentina) - National Institute of Informatics (Japan)} 
\date{} 
%\subject{} 
%-------------------------------------------------------------------------
\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\tableofcontents
\end{frame}

%-------------------------------------------------------------------------
\section{Introduction}
\begin{frame}{Introduction}

Our research went through multiple stages. Starting with Linked Open Data, moving to Social Network Analysis and ending with applied machine learning.
\vspace{15pt}

Thus the order of this presentation will be chronological.
\vspace{15pt}

Nonetheless our main focus is: \emph{Social network of seiyuu} (or anime's voice actors)
\end{frame}
%-------------------------------------------------------------------------
\section{Dataset}
\input{dataset}
%-------------------------------------------------------------------------
\section{Social Network}
\input{socialNetwork}
%-------------------------------------------------------------------------
\section{Popularity}
\input{popularity}
%-------------------------------------------------------------------------
\section{Conclusion}
\begin{frame}{Conclusion}
Popularity prediction and analysis will remain an open question for now since we couldn't get good results with our reduced data and time.\\

But as far as we know this is the first time a \emph{social network of seiyuu} and anime is analyzed, we still could get a hold of

\begin{itemize}
\item state of the art of seiyuu and anime data; which is very incomplete or withouth good format.
\item structure and characteristics about seiyuu's social network.
\item the need of more and better quality data for understanding popularity of seiyuu.
\end{itemize}
\end{frame}
%-------------------------------------------------------------------------

\begin{frame}{Future works and Thanks!}
Future works:
\begin{itemize}
\item Compare social network growth with particular graphs to see in which category it fits.
\item Improve models and data, try new approachs to improve popularity predictions and analysis.
\item Organize seiyuu and anime data using Wikidata ontology and make it open.
\end{itemize}
\vspace{15pt}

{\Large \emph{Thank you for your attention, feel free to ask questions!}}
\end{frame}
%-------------------------------------------------------------------------

\end{document}